Indel Historian: phylogenetic ancestral reconstruction

### 2016-07-21 doc/main.tex
writeup

Here, we present a clean implementation of the algorithm underlying ProtPal
in a new tool, Indel Historian, which we recommend for evolutionary applications such
as ancestral sequence reconstruction and molecular phylogenetics

@@

Comparison to MCMC tools

@@

>>>>

Here, we present a clean implementation of the algorithm underlying ProtPal
in a new tool, Indel Historian
The tool is targeted to evolutionary applications such
as ancestral sequence reconstruction and molecular phylogenetics

@@

Comparison to MCMC tools
BaliPhy, PhylogenyCafe, HandAlign

@@

\section{Discussion}

The best-performing method MUSCLE introduces heuristics into its scoring scheme
that improve accuracy.

It is harder to incorporate these sorts of modifications into a rigorous phylogenetic model
primarily because they violate the assumption of independence
between indel and substitution processes
that most such models rely on

Decision theory may also be useful in conjunction with MCMC tools \cite{HermanHeinEtc}
